Age-related changes in plant growth and traits

### 2015-09-09 RA_combined_plots.Rmd
Small bits of work on RA schedule figures

>>>>

#modified; original below
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
pdf("figs2/RA_schedule_plots", height=11.3, width=8)
plot
par(mfcol=c(4,2), cex=1, omi=c(.1,.2,.3,.1), mai=c(.6,.6,.1,0.1)) 
yvar <- "leaf_area"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

data2 <- subset(SummarySppAge[["mean"]])
data2 <- split(data2, data2$species)

  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="leaf area (midyear)",ylab="total investment (mg)",cex=1.3,
                    col=col.age(data[[spp]]$age),main=spp)
  arrows(data[[spp]]$leaf_area_midyear,data[[spp]]$growth_inv,data[[spp]]$leaf_area_midyear,data[[spp]]$total_inv,length = 0, angle = 30, code = 2, col = "black",lwd=1)
  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="age",ylab="RA",cex=1.3,ylim=c(0,1.4),
                    col=col.age(data[[spp]]$age))
  points(RA_leaf_area~age,data2[[spp]],pch=16)
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="xy",xlab="age",ylab="final leaf area",cex=1.3,
                    col=col.age(data[[spp]]$age))
  points(leaf_area~age,data2[[spp]],pch=16)
  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar2,log="xy",xlab="age",ylab="height",cex=1.3,
                    col=col.age(data[[spp]]$age))
  points(height~age,data2[[spp]],pch=16)
  }
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
par(mfcol=c(2,2), cex=1, omi=c(.1,.3,.3,.1), mai=c(1.1,1,.1,0.1)) 
xvar <- "age"

yvar1 <- "height"
yvar2 <- "diameter"
yvar3 <- "leaf_area"
yvar4 <- "total_weight_0"

  plot_yvar_vs_xvar(data[[spp]], yvar1, xvar,log="xy",ylab="height",xlab="age",cex=1.3,
                    col=col.age(data[[spp]]$age),main=spp)
  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar,log="xy",ylab="diameter",xlab="",cex=1.3,
                    col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",ylab="leaf area",xlab="",cex=1.3,
                    col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar,log="xy",ylab="weight",xlab="",cex=1.3,
                    col=col.age(data[[spp]]$age))
  }
```

### 2015-09-09 tests.Rmd
Small bits of work on RA schedule figures

>>>>

for(spp in names(data)) {
plot(stem_weight~diameter,data[[spp]],log="xy",cex=1.3, main=spp,col=col.age(data[[spp]]$age),pch=16)
points(stem_weight_0~diameter_0,data[[spp]],cex=1.3,pch=1,col=col.age(data[[spp]]$age))
arrows(data[[spp]]$diameter, data[[spp]]$stem_weight, data[[spp]]$diameter_0,data[[spp]]$stem_weight_0, length = 0,angle = 30, code = 2, col = col.age(data[[spp]]$age),lwd=.3)
points(leaf_weight~diameter,data[[spp]],cex=1.3,pch=17,col=col.age(data[[spp]]$age))
points(leaf_weight_0~diameter_0,data[[spp]],cex=1.3,pch=2,col=col.age(data[[spp]]$age))
arrows(data[[spp]]$diameter, data[[spp]]$leaf_weight, data[[spp]]$diameter_0,data[[spp]]$leaf_weight_0, length = 0,angle = 30, code = 1, col = col.age(data[[spp]]$age),lwd=.3,lty=3)
}+
```
